Incentivizing Exploration with Unbiased Histories

### 2019-02-01 COLT 2019 Submission/3level.tex
Lots of minor space-saving edits.

\begin{theorem}
\label{thm:3level}
For two arms, the three-level policy
achieves regret
\[ \reg(T) \leq O\left( T^{4/7}\, \log T \right).\]
This is achieved with parameters
    $T_1 = T^{4/7}\log^{-1/7}(T)$,
    $\NG = 2^{10}\log(T)$, and
    $T_2 = T^{6/7}\log^{-5/7}(T)$.
\end{theorem}

@@

\xhdr{The ``good events".}
We establish four ``good events" each of which occurs with high probability.
\begin{description}
\item[(\event{1})] \emph{Exploration in Level 1:} Every first-level group collects  $\Omega(T_1)$ samples of each arm.
\item[(\event{2})] \emph{Concentration in Level 1:} Within each first-level group, empirical mean rewards of each arm $a$ concentrate around $\mu_a$.
\item[(\event{3})] \emph{Anti-concentration in Level 1:} For each arm, some first-level subgroup collects data which makes this arm look much better than its actual mean and other arms look worse than their actual means.
\item[(\event{4})] \emph{Concentration in prefix:}
Empirical mean reward of each arm $a$ concentrates around $\mu_a$ in any prefix of its pulls (ensuring accurate reward estimates in exploitation.)
\end{description}

>>>>

\begin{theorem}
\label{thm:3level}
For two arms, the three-level policy
achieves regret
$ \reg(T) \leq O\left( T^{4/7}\, \log T \right)$.
This is achieved with parameters
    $T_1 = T^{4/7}\log^{-1/7}(T)$,
    $\NG = 2^{10}\log(T)$, and
    $T_2 = T^{6/7}\log^{-5/7}(T)$.
\end{theorem}

@@

\xhdr{The ``good events".}
We establish four ``good events" which occur with high probability.
\begin{description}
\item[(\event{1})] \emph{Exploration in Level 1:} Every first-level group collects  $\Omega(T_1)$ samples of each arm.
\item[(\event{2})] \emph{Concentration in Level 1:} Within each first-level group, empirical mean rewards of each arm $a$ concentrate around $\mu_a$.
\item[(\event{3})] \emph{Anti-concentration in Level 1:} For each arm, some first-level subgroup collects data which makes this arm look much better than its actual mean and other arms look worse than their actual means.
\item[(\event{4})] \emph{Concentration in prefix:}
Empirical mean reward of each arm $a$ concentrates around $\mu_a$ in any prefix of its pulls (ensuring accurate reward estimates in exploitation.)
\end{description}

### 2019-02-01 COLT 2019 Submission/intro.tex
Lots of minor space-saving edits.

The main challenge is that the agents still follow exploitation-only behavior, just like they do for the full-disclosure policy, albeit based only on a portion of history. A disclosure policy controls the flow of information (who sees what), but not the \emph{content} of that information.

>>>>

The main challenge is that the agents still follow exploitation-only behavior, as for the full-disclosure policy, albeit based only on a portion of history. A disclosure policy controls the flow of information (who sees what), but not the \emph{content} of that information.

### 2019-02-01 COLT 2019 Submission/llevel-overview.tex
Lots of minor space-saving edits.

% In Theorem \ref{thm:llevel-1}, we show our $L$-level policy. We can
% achieve nearly optimal regret $O_K(T^{1/2} \polylog(T))$ with
% $O(\log\log(T))$ levels.
\begin{theorem}
\label{thm:llevel-1}
For any $L > 3$, there exists an $L$-level disclosure policy with
regret $$O_K\left(T^{2^{L-1}/(2^L-1)} \cdot \polylog(T) \right).$$ In
particular, there exists a $O(\log\log(T))$-level recommendation
policy with regret $O_K(T^{1/2} \polylog(T))$.
\end{theorem}

@@

\begin{theorem}
\label{thm:llevel-2}
There exists an $O(\log(T)/\log\log(T))$-level policy such that for
every multi-armed bandit instance with gap parameter $\Delta$, the
policy has regret $$O_K(\min(1/\Delta, T^{1/2}) \cdot \polylog(T))$$
Moreover, under this policy, each agent $t$ observes a subhistory of
size at least $\Omega( t/\polylog(T))$.
\end{theorem}

>>>>

% In Theorem \ref{thm:llevel-1}, we show our $L$-level policy. We can
% achieve nearly optimal regret $O_K(T^{1/2} \polylog(T))$ with
% $O(\log\log(T))$ levels.
\begin{theorem}
\label{thm:llevel-1}
For any $L > 3$, there is an $L$-level disclosure policy with
regret 
    $O_K\left(T^{2^{L-1}/(2^L-1)} \cdot \polylog(T) \right)$.
 In particular, there is a $O(\log\log(T))$-level recommendation
policy with regret $O_K(T^{1/2} \polylog(T))$.
\end{theorem}

@@

\begin{theorem}
\label{thm:llevel-2}
There exists an $O(\log(T)/\log\log(T))$-level policy such that for
every multi-armed bandit instance with gap parameter $\Delta$, the
policy has regret 
    $O_K(\min(1/\Delta, T^{1/2}) \cdot \polylog(T))$
Moreover, under this policy, each agent $t$ observes a subhistory of
size at least $\Omega( t/\polylog(T))$.
\end{theorem}

### 2019-02-01 COLT 2019 Submission/related-work.tex
Lots of minor space-saving edits.

Full-disclosure policy, and closely related ``greedy" (exploitation-only) algorithm in multi-armed bandits, have been a subject of a recent line of work \citep{Sven-aistats18,kannan2018smoothed,bastani2017exploiting,externalities-colt18}.
A common theme is that the greedy algorithm performs well in theory, under  substantial assumptions on heterogeneity of the agents. Yet, it suffers $\Omega(T)$ regret in the worst case.%
\footnote{This is a well-known folklore result; \eg see \citep{CompetingBandits-itcs18} for a concrete example.}
\citet{Baransi-ecml14} use the ``greedy" algorithm on randomly sub-sampled subhistories to achieve optimal regret rate for two arms. However, their result is insufficient for our motivation, as the subhistories are not \emph{unbiased} or \emph{transitive}, in the sense defined earlier in the Introduction. In particular, the sub-sampling scheme depends on the current history, which may distort agents' incentives.

>>>>

Full-disclosure policy, and closely related ``greedy" (exploitation-only) algorithm in multi-armed bandits, have been a subject of a recent line of work \citep{Sven-aistats18,kannan2018smoothed,bastani2017exploiting,externalities-colt18}.
A common theme is that the greedy algorithm performs well in theory, under  substantial assumptions on heterogeneity of the agents. Yet, it suffers $\Omega(T)$ regret in the worst case.%
\footnote{This is a well-known folklore result; \eg see \citep{CompetingBandits-itcs18} for a concrete example.}
\citet{Baransi-ecml14} use the ``greedy" algorithm on randomly sub-sampled subhistories to achieve optimal regret rate for two arms. However, their result is insufficient for our motivation, as the subhistories are not \emph{unbiased} or \emph{transitive}, in the sense defined earlier. In particular, the sub-sampling scheme depends on the history, which may distort agents' incentives.
